---
title: "Writing_Functions.Rmd"
author: "Briana Lettsome"
date: "November 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

set.seed(1)
```

```{r}
x = rnorm(25, mean = 5, sd = 3)

(x - mean(x)) / sd(x)

z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x)
```


z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}

```

```{r}
# Is this supposed to make a plot. It does not work. Why?
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```


```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

```



```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


```{r}
extract_reviews = function(url) {
  dynamite_html = read_html(url)
  review_titles = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  review_stars = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"
extract_reviews(url)

```




